We used an anonymous marketplace product listing dataset created by the researcher known as
Gwern\cite{gwern-darknet}.
This dataset was created by crawling several marketplaces daily, from June 6th, 2014 to July 7th, 2015.
For each product listing, we extracted the posting text, including name and description.
The resulting dataset was then cleaned to remove parse errors and duplicate listings.
We then tokenized the cleaned listings by extracting all words and numbers seperated by spaces or
symbols.
The final dataset had about 84,000 unique product listings and was used as input to feature extraction.

\begin{table}[!ht]
    \begin{center}
        \begin{tabular}{| l | p{0.8\linewidth} |}
        \hline
        Crawl Date & 2014-06-28 \\
        \hline
        Category & MDMA \\
        \hline
        Title & 28 Grams of Interways Crystal Clear Molly \\
        \hline
        Price & 1.37853692 BTC \\
        \hline
        Description & This is 28 grams of Interways crystal clear molly.
        It will be both rocky and sandy as thats how I received it.
        I am pre packaging these up accordingly and only cr... \\
        \hline
        \end{tabular}
    \end{center}
    \caption{Example product listing on Agora}
\end{table}

To convert the text to features, we used Term Frequecy-Inverse Document Frequence (TF-IDF).
TF-IDF converts each token in the listing to a token weight based on how important that token is to the listing, normalized by the number of times the token appears in the whole corpus.
This normalization helps to reduce the impact of common token in the corpus.
Finally, each listing is then converted to a vector of token weights, similar to word2vec.

$$ {tf}_{t,d} = \text{number of times token } t \text{ appears in document } d $$
$$ {idf}_t = \log \frac{\text{total number of documents}}{\text{number of documents the token } t \text{ appears in}} $$
$$ w_{t,d} = (1 + \log ({tf}_{t,d})) * (1 + {idf}_t) $$

Additionally, we manually labeled about 500 product listings to train our classifier as well as to use for cross-validation.
We classified each product listing into one of twelve categories.
These product categories were derived from the product categories on both Agora\cite{agora} (one of the largest anonymous markets) and /r/darknetmarkets (a popular forum for advertising and discussing drugs).
